---
title: "Bootstrapping"
author: "Korawat Tanwisuth"
date: "August 3, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r, message=FALSE, warning=FALSE}
library(quantmod)
library(mosaic)
library(foreach)
library(pander)
# start <- as.Date("2007-01-01")
# end <- as.Date("2017-01-01")
# mys
# getSymbols("SPY", src = "yahoo", from =start, to = end)
# getSymbols("TLT", src = "yahoo", from =start, to = end)
# getSymbols("LQD", src = "yahoo", from =start, to = end)
# getSymbols("EEM", src = "yahoo", from =start, to = end)
# getSymbols("VNQ", src = "yahoo", from =start, to = end)
```


```{r}
mystocks <- c("SPY", "TLT", "LQD", "EEM", "VNQ")
getSymbols(mystocks)
SPYa <- adjustOHLC(SPY)
TLTa <- adjustOHLC(TLT)
LQDa <- adjustOHLC(LQD)
EEMa <- adjustOHLC(EEM)
VNQa <- adjustOHLC(VNQ)
myreturns <- cbind(ClCl(SPY),ClCl(TLT),ClCl(LQD),ClCl(EEM),ClCl(VNQ))
myreturns <- as.matrix(na.omit(myreturns))
```


```{r}
# computereturns = function(series) {
# 
# 	mycols = grep('Adjusted', colnames(series))
# 	myorder = order(rownames(series))
# 	series = series[myorder,]
# 
# 	closingprice = series[,mycols]
# 
# 	N = nrow(closingprice)
# 	myrownames = rownames(series)[1:(N-1)]
# 
# 	percentreturn = as.data.frame(closingprice[2:N,]) / as.data.frame(closingprice[1:(N-1),]) - 1
# 
# 	mynames = strsplit(colnames(percentreturn), '.', fixed=TRUE)
# 
# 	mynames = lapply(mynames, function(x) return(paste0(x[1], ".PctReturn")))
# 
# 	colnames(percentreturn) = mynames
# 	rownames(percentreturn) = myrownames
# 
# 	na.omit(percentreturn)
# 
# }
```

```{r}
#Get return on each of the assest
# myprices <- data.frame(cbind(SPY,TLT,LQD,EEM,VNQ))
# myreturns <- computereturns(myprices)
```

```{r}
asset_return <- sort(apply(myreturns, 2,mean))
asset_risk <- sort(apply(myreturns, 2, sd))
```


### Expected Return for each asset 
```{r}
pander(asset_return)
```

Now, we rank the five asset from lowest return to highest return based on sample mean.

### Standard deviation of return for each asset
```{r}
pander(asset_risk)
```

Here, we rank them from lowest risk to highest risk based on sample standard deviations.

From the above tables, we can classify our assets into different categories. Any assets below the 3rd rank will be given a score low. Those above the third rank will be given a score high, and the middle rank will be given a score medium.

**SPY** - High return/ Medium risk 

**TLT** - Medium return/ Low risk

**LQD** - Low return/ Low risk

**EEM** - Low return/ High risk

**VNQ** - High return/ High risk


```{r}
sim_stock <- function(myreturns, investment, endperiod, weights, num_sim){
    sim_result <- do(num_sim) * {
        totalwealth <- investment #reset totalwealth for every simulation
        horizon <- endperiod
        holdings <- weights * totalwealth
        for (today in 1:horizon) {
            return_today <- resample(myreturns, 1, orig.ids = FALSE)
            holdings <- holdings + return_today * holdings
            totalwealth <- sum(holdings)
            holdings <- weights * totalwealth #end of day. redistribute the wealth
        }
        totalwealth
    }
    
}

```

### Setting values for our simulation

We have 100,000 to invest, and we will do our simulation for 20 days.

```{r}
investment <- 100000
endperiod <- 20
```

For each of the strategy, we will adjust the weight accordingly.

### Even Split Strategy

We will assign equal weights to all five assets

```{r}
set.seed(1)
weights <- c(0.2,0.2,0.2,0.2,0.2)
even_strategy <- sim_stock(myreturns, investment, endperiod, weights, 3000)
```


### Safe Strategy

For this strategy, we will look at our classification of the five assets and choose those with low risk properties. We will also include one medium risk asset. For the weight, we will use 1/standard deviation as the coefficients and normalize them to add up to 1. SPY, TLT, and LQD are the three chosen assets. 
```{r}
set.seed(1)
spy_coef <- 1/asset_risk[3]
tlt_coef <- 1/asset_risk[2]
lqd_coef <- 1/ asset_risk[1]
total_coef <- spy_coef + tlt_coef + lqd_coef
spy_coef <- spy_coef/total_coef
tlt_coef <- tlt_coef/total_coef
lqd_coef <- lqd_coef/total_coef
weights <- c(spy_coef, tlt_coef,lqd_coef, 0, 0)
safe_strategy <- sim_stock(myreturns, investment, endperiod, weights, 3000)
```


### Aggressive Strategy

For this strategy, we will not be as diversified as the safe strategy. Also, we will look mainly at assests which have high returns with moderate to high risks. Coefficients will be adjusted based on the expected return values. We will invest in SPY and VNQ

```{r}
set.seed(1)
total_coef_a <- asset_return[4] + asset_return[5]
spy_coef_a <- asset_return[4]/total_coef_a
vnq_coef_a <- asset_return[5]/total_coef_a
weights <- c(spy_coef_a, 0, 0, 0, vnq_coef_a)
aggressive_strategy <- sim_stock(myreturns, investment, endperiod, weights, 3000)
```


###Distribution of return values for even split strategy


```{r}
profit_split <- even_strategy$result - 100000
var05_split <- qdata(profit_split, 0.05)[2]
hist(profit_split, 60,col = "cornsilk", xlab = "Return values", main = "Distribution of Return Values (Even Split Strategy)")
abline(v = var05_split, col = "firebrick", lwd = 3)
abline(v = mean(profit_split), col = "cyan4", lwd = 3)
legend("topright", 
       c("5% value at risk", "expected return"), 
       lty=c(1, 1), 
       col=c("firebrick","cyan4"), 
       bty = "n")
```



```{r}
var_mean_split <- c(var05_split, mean(profit_split))
names(var_mean_split) <- c("Value at Risk at 5%", "Expected Return")
pander(var_mean_split)
```


###Distribution of return values for safe strategy


```{r}
profit_safe <- safe_strategy$result - 100000
var05_safe <- qdata(profit_safe, 0.05)[2]
hist(profit_safe, 60,col = "cornsilk", xlab = "Return values", main = "Distribution of Return Values (Safe Strategy)")
abline(v = var05_safe, col = "firebrick", lwd = 3)
abline(v = mean(profit_safe), col = "cyan4", lwd = 3)
legend("topright", 
       c("5% value at risk", "expected return"), 
       lty=c(1, 1), 
       col=c("firebrick","cyan4"), 
       bty = "n")
```


```{r}
var_mean_safe <- c(var05_safe, mean(profit_safe))
names(var_mean_safe) <- c("Value at Risk at 5%", "Expected Return")
pander(var_mean_safe)
```

###Distribution of return values for agressive strategy


```{r}
profit_aggressive <- aggressive_strategy$result - 100000
var05_aggressive <- qdata(profit_aggressive, 0.05)[2]
hist(profit_aggressive, 60,col = "cornsilk", xlab = "Return values", main = "Distribution of Return Values (Aggressive Strategy)")
abline(v = var05_aggressive, col = "firebrick", lwd = 3)
abline(v = mean(profit_aggressive), col = "cyan4", lwd = 3)
legend("topright", 
       c("5% value at risk", "expected return"), 
       lty=c(1, 1), 
       col=c("firebrick","cyan4"), 
       bty = "n")
```


```{r}
var_mean_aggressive <- c(var05_aggressive, mean(profit_aggressive))
names(var_mean_aggressive) <- c("Value at Risk at 5%", "Expected Return")
pander(var_mean_aggressive)
```