---
title: "market segmentation"
author: "Yue"
date: "8/8/2017"
output: html_document
---

```{r }
#have a brief idea of the data
setwd("~/Desktop/summer 2017/predictive modelling/second half/STA380-master/data")
mkt = read.csv("social_marketing.csv")
summary(mkt)
dim(mkt)
colSums(mkt[2:37])
```

```{r}
#change the first column into index
mkt2 = mkt[,-1]
rownames(mkt2) <- mkt[,1]
```

```{r}
#drop some categories that are not meaningful
drops <- c("chatter", "uncategorized", "spam", "adult")
mkt3 = mkt2[ , !(names(mkt2) %in% drops)]
sum = colSums(mkt3)
sum
sum2 = sort(sum, decreasing = TRUE)
sum2
```

```{r}
#scale the data
mkt_scaled <- scale(mkt3, center=TRUE, scale=TRUE) 
```

```{r}
#before using k-means, lets find the best k using elbow function
wss <- (nrow(mkt_scaled)-1)*sum(apply(mkt_scaled,2,var))
for (i in 2:15) wss[i] <- sum(kmeans(mkt_scaled, centers=i)$withinss)
plot(1:15, wss, type="b", xlab="Number of Clusters", ylab="Within groups sum of squares")
```

```{r}
#use 10 clusters
cluster_all <- kmeans(mkt_scaled, centers=10, nstart=50)
```

```{r}
#add cluster to original data
mkt3$cluster <- as.numeric(cluster_all$cluster)
```

```{r}
#Frequency of each cluster
table(mkt3$cluster)
```

```{r}
#creating individual datasets for analysis 
#drop the four useless categories
social_group1 = mkt[mkt3$cluster==1,c(2:37)]
social_group1 = social_group1[ , !(names(social_group1) %in% drops)]

social_group2 = mkt[mkt3$cluster==2,c(2:37)]
social_group2 = social_group2[ , !(names(social_group2) %in% drops)]

social_group3 = mkt[mkt3$cluster==3,c(2:37)]
social_group3 = social_group3[ , !(names(social_group3) %in% drops)]

social_group4 = mkt[mkt3$cluster==4,c(2:37)]
social_group4 = social_group4[ , !(names(social_group4) %in% drops)]

social_group5 = mkt[mkt3$cluster==5,c(2:37)]
social_group5 = social_group5[ , !(names(social_group5) %in% drops)]

social_group6 = mkt[mkt3$cluster==6,c(2:37)]
social_group6 = social_group6[ , !(names(social_group6) %in% drops)]

social_group7 = mkt[mkt3$cluster==7,c(2:37)]
social_group7 = social_group7[ , !(names(social_group7) %in% drops)]

social_group8 = mkt[mkt3$cluster==8,c(2:37)]
social_group8 = social_group8[ , !(names(social_group8) %in% drops)]

social_group9 = mkt[mkt3$cluster==9,c(2:37)]
social_group9 = social_group9[ , !(names(social_group9) %in% drops)]

social_group10 = mkt[mkt3$cluster==10,c(2:37)]
social_group10 = social_group10[ , !(names(social_group10) %in% drops)]

```

```{r}
#plot each group
library(ggplot2)
qplot(x=names(social_group1), y=apply(social_group1, MARGIN=2, FUN=mean), xlab='Category',ylab='Average occurences') + geom_bar(stat = 'identity', fill = "firebrick2", color = "firebrick4")+ theme(axis.text.x = element_text(angle=90, hjust=1))
```
groups: politics, travel, computers
segment: high-educated people who like high technology

```{r}
qplot(x=names(social_group2), y=apply(social_group2, MARGIN=2, FUN=mean), xlab='Category',ylab='Average occurences') + geom_bar(stat = 'identity', fill = "firebrick2", color = "firebrick4")+ theme(axis.text.x = element_text(angle=90, hjust=1))
```
groups: sports_fandom, religion, food, parenting
market segment: parents who like sports???

```{r}
qplot(x=names(social_group3), y=apply(social_group3, MARGIN=2, FUN=mean), xlab='Category',ylab='Average occurences') + geom_bar(stat = 'identity', fill = "firebrick2", color = "firebrick4")+ theme(axis.text.x = element_text(angle=90, hjust=1))
```
groups: photo_sharing, shopping, current-events
market segmentation: young ladies who like fashion, catch up the trend


```{r}
qplot(x=names(social_group4), y=apply(social_group4, MARGIN=2, FUN=mean), xlab='Category',ylab='Average occurences') + geom_bar(stat = 'identity', fill = "firebrick2", color = "firebrick4")+ theme(axis.text.x = element_text(angle=90, hjust=1))
```
groups: news, politics, automotive
market segment: mature male


```{r}
qplot(x=names(social_group5), y=apply(social_group5, MARGIN=2, FUN=mean), xlab='Category',ylab='Average occurences') + geom_bar(stat = 'identity', fill = "firebrick2", color = "firebrick4")+ theme(axis.text.x = element_text(angle=90, hjust=1))
```
groups: cooking, fashion, photo_sharing, beauty
market segment: young ladies, esp young mom


```{r}
qplot(x=names(social_group6), y=apply(social_group6, MARGIN=2, FUN=mean), xlab='Category',ylab='Average occurences') + geom_bar(stat = 'identity', fill = "firebrick2", color = "firebrick4")+ theme(axis.text.x = element_text(angle=90, hjust=1))
```
groups: dating, photo sharing
market segment: young people

```{r}
qplot(x=names(social_group7), y=apply(social_group7, MARGIN=2, FUN=mean), xlab='Category',ylab='Average occurences') + geom_bar(stat = 'identity', fill = "firebrick2", color = "firebrick4")+ theme(axis.text.x = element_text(angle=90, hjust=1))
```
groups: college_uni, online_gaming
market segmentation: college students who like gaming

```{r}
qplot(x=names(social_group8), y=apply(social_group8, MARGIN=2, FUN=mean), xlab='Category',ylab='Average occurences') + geom_bar(stat = 'identity', fill = "firebrick2", color = "firebrick4")+ theme(axis.text.x = element_text(angle=90, hjust=1))
```
groups: tv_film, art, college_uni
market segment: people who like arts

```{r}
qplot(x=names(social_group9), y=apply(social_group9, MARGIN=2, FUN=mean), xlab='Category',ylab='Average occurences') + geom_bar(stat = 'identity', fill = "firebrick2", color = "firebrick4")+ theme(axis.text.x = element_text(angle=90, hjust=1))
```
groups: health_nutrition, personal_fitness, cooking
market segment: people who care fitness

```{r}
qplot(x=names(social_group10), y=apply(social_group10, MARGIN=2, FUN=mean), xlab='Category',ylab='Average occurences') + geom_bar(stat = 'identity', fill = "firebrick2", color = "firebrick4")+ theme(axis.text.x = element_text(angle=90, hjust=1))
```
groups: photo_sharing, current_events, health_nutrition, travel
market segment: 

Overall, the target should be young people, well-educated people, who cares social, fashion, fitness, current events. 

