---
title: "market segmentation"
author: "Yue"
date: "8/8/2017"
output: md_document
---
# Market Segmentation

# Descriptives and Initial Analysis
```{r }
#have a brief idea of the data
mkt = read.csv("~/Downloads/social_marketing.csv")
dim(mkt)
set.seed(123)
library(ggplot2)
```

```{r}
#change the first column into index
mkt2 = mkt[,-1]
rownames(mkt2) <- mkt[,1]
```

```{r}
#drop some categories that are not meaningful
drops <- c("chatter", "uncategorized", "spam", "adult")
mkt3 = mkt2[ , !(names(mkt2) %in% drops)]

#get an initial look at the frequencies of each category
sum = colSums(mkt3)
sum2 = sort(sum, decreasing = TRUE)
sum2
```

```{r}
#scale the data
mkt_scaled <- scale(mkt3, center=TRUE, scale=TRUE) 
```

# Decide how many clusters we should use
```{r}
# Use different methods to decide how many clusters we should use
# CH index method: try to maximize the CH index
error_vec <- rep(0,20)
ch_index <- rep(0,20)
# clusplot(social, social_cluster$cluster, color = T, shade = T, labels = 0, lines = 0)
for(k in 1:20) {
    social_cluster <- kmeans(mkt_scaled, k, nstart = 25)
    error_vec[k] <- social_cluster$tot.withinss
    ch_index[k] <-(sum(social_cluster$betweenss)/(k - 1))/(sum(social_cluster$withinss)/(sum(social_cluster$size)- k))
}

ch_index <- data.frame(ch_index)
ch_index <- cbind(1:nrow(ch_index),ch_index)
colnames(ch_index) <- c("K","CH_index")
ggplot(ch_index, aes(x=K, y = CH_index)) + geom_point(aes(size = CH_index,color = "size = 2"),show.legend = FALSE) + xlab("K (Complexity)") +ylab("CH_index")+ scale_size_continuous(range = c(3, 9)) + geom_vline(aes(xintercept=2,colour="selected K") ,size =1.5) + 
scale_colour_manual(name="",values=c("selected K"= "cyan4", "size = 2"="salmon"))
```
When using the CH index to decide the optimal number of clusters, we need to maximize the CH index to achieve the balance between fit and complexity. The graph above suggests that we need to use 2 clusters in the kmeans clustering method. 

```{r}
# Use the percentage reduction method
error_vec_shift <- c(0,error_vec)[-21]
percent_change <- data.frame((1-(error_vec/error_vec_shift))[-1]*100)
percent_change <- cbind(2:length(error_vec),percent_change)
colnames(percent_change) <- c("K","Percent_Change")
ggplot(percent_change, aes(x=K, y = Percent_Change)) + geom_point(aes(size = Percent_Change,color = "size = 6"),show.legend = FALSE) + xlab("K (Complexity)") +ylab("% Decrease in Error")+ scale_size_continuous(range = c(3, 9)) + geom_vline(aes(xintercept=6,colour="selected K") ,size =1.5) + 
scale_colour_manual(name="",values=c("selected K"= "cyan4", "size = 6"="salmon"))
```
When using the percentage reducation method, we try to choose the number of clusters that reduces the error percentage the most. Each dot in the graph means the change from n cluster to n+1 cluster. Result suggests that when the cluster increases from 5 to 6, the error percentage decreases the most. Then, we should use 6 clusters.


```{r}
# find the best k using elbow function
wss <- (nrow(mkt_scaled)-1)*sum(apply(mkt_scaled,2,var))
for (i in 2:15) wss[i] <- sum(kmeans(mkt_scaled, centers=i)$withinss)

wss <- data.frame(wss)
wss <- cbind(1:nrow(wss),wss)
colnames(wss) <- c("K","wss")
ggplot(wss, aes(x=K, y = wss)) + geom_point(aes(size = wss,color = "size = 10"),show.legend = FALSE) + xlab("K (Complexity)") +ylab("Within groups sum of squares")+ scale_size_continuous(range = c(3, 9)) + geom_vline(aes(xintercept=10,colour="selected K") ,size =1.5) + 
scale_colour_manual(name="",values=c("selected K"= "cyan4", "size = 10"="salmon"))

```
When looking within groups sum of squares, we find difficult to decide the optimal number of ks to use as the cutoff. As when there are more clusters, the within groups of squared error would decrease. However, since this curve is convex, and the slope after k=10 becomes more flatter. So we feel that k=10 is the optimal for this method. However, since we only have 32 categories after cleaning, and 10 clusters are too many. 

Therefore, we decide to look at two conditions, where k equals 2 and 6 separately, and discuss the market segmentation. 

# Use 2 clusters
```{r}
#use 2 clusters
cluster_all_2 <- kmeans(mkt_scaled, centers=2, nstart=50)
```

```{r}
#add cluster to original data
mkt3$cluster <- as.numeric(cluster_all_2$cluster)
```

```{r}
#Frequency of each cluster
table(mkt3$cluster)
```

```{r}
#creating individual datasets for analysis 
#drop the four useless categories
social_group1_2cluster = mkt[mkt3$cluster==1,c(2:37)]
social_group1_2cluster = social_group1_2cluster[ , !(names(social_group1_2cluster) %in% drops)]

social_group2_2cluster = mkt[mkt3$cluster==2,c(2:37)]
social_group2_2cluster = social_group2_2cluster[ , !(names(social_group2_2cluster) %in% drops)]
```

```{r}
#plot each group: group 1

#sort the frequency for each category
mean_social_group1_2cluster = apply(social_group1_2cluster, MARGIN=2, FUN=mean)
mean_social_group1_2cluster= sort(mean_social_group1_2cluster, decreasing = TRUE)
mean_social_group1_2cluster = data.frame(cbind(names(mean_social_group1_2cluster),unname(mean_social_group1_2cluster)))

colnames(mean_social_group1_2cluster) <- c("category", "frequency")
mean_social_group1_2cluster$frequency <- as.numeric(as.character(mean_social_group1_2cluster$frequency))

# plot
ggplot(mean_social_group1_2cluster, aes(x=reorder(category,frequency),y=frequency)) + geom_bar(stat = 'identity', fill = "salmon", color ="white")+ coord_flip() + theme(axis.text.x = element_text(angle=90, hjust=1))
```

> category: health_nutrition, cooking, photo_sharing, sports_fandom
> market segmentation: well-educated people, especially young people

```{r}
#plot each group: group 2

#sort the frequency for each category
mean_social_group2_2cluster = apply(social_group2_2cluster, MARGIN=2, FUN=mean)
mean_social_group2_2cluster= sort(mean_social_group2_2cluster, decreasing = TRUE)
mean_social_group2_2cluster = data.frame(cbind(names(mean_social_group2_2cluster),unname(mean_social_group2_2cluster)))

colnames(mean_social_group2_2cluster) <- c("category", "frequency")
mean_social_group2_2cluster$frequency <- as.numeric(as.character(mean_social_group2_2cluster$frequency))

# plot
ggplot(mean_social_group2_2cluster, aes(x=reorder(category,frequency),y=frequency)) + geom_bar(stat = 'identity', fill = "salmon", color ="white")+ coord_flip() + theme(axis.text.x = element_text(angle=90, hjust=1))
```
> category: photo_sharing, health_nutrition, current_events, politics, travel, cooking, college_uni
> market segmentation: 

# Use 6 clusters:

```{r}
#use 10 clusters
cluster_all_6cluster <- kmeans(mkt_scaled, centers=6, nstart=50)
```

```{r}
#add cluster to original data
mkt3$cluster <- as.numeric(cluster_all_6cluster$cluster)
```

```{r}
#Frequency of each cluster
table(mkt3$cluster)
```

```{r}
#creating individual datasets for analysis 
#drop the four useless categories
social_group1_6cluster = mkt[mkt3$cluster==1,c(2:37)]
social_group1_6cluster = social_group1_6cluster[ , !(names(social_group1_6cluster) %in% drops)]

social_group2_6cluster = mkt[mkt3$cluster==2,c(2:37)]
social_group2_6cluster = social_group2_6cluster[ , !(names(social_group2_6cluster) %in% drops)]

social_group3_6cluster = mkt[mkt3$cluster==3,c(2:37)]
social_group3_6cluster = social_group3_6cluster[ , !(names(social_group3_6cluster) %in% drops)]

social_group4_6cluster = mkt[mkt3$cluster==4,c(2:37)]
social_group4_6cluster = social_group4_6cluster[ , !(names(social_group4_6cluster) %in% drops)]

social_group5_6cluster = mkt[mkt3$cluster==5,c(2:37)]
social_group5_6cluster = social_group5_6cluster[ , !(names(social_group5_6cluster) %in% drops)]

social_group6_6cluster = mkt[mkt3$cluster==6,c(2:37)]
social_group6_6cluster = social_group6_6cluster[ , !(names(social_group6_6cluster) %in% drops)]
```

```{r}
#plot each group: group 1

#sort the frequency for each category
mean_social_group1_6cluster = apply(social_group1_6cluster, MARGIN=2, FUN=mean)
mean_social_group1_6cluster= sort(mean_social_group1_6cluster, decreasing = TRUE)
mean_social_group1_6cluster = data.frame(cbind(names(mean_social_group1_6cluster),unname(mean_social_group1_6cluster)))

colnames(mean_social_group1_6cluster) <- c("category", "frequency")
mean_social_group1_6cluster$frequency <- as.numeric(as.character(mean_social_group1_6cluster$frequency))

ct=cluster_all_6cluster$centers[1,]
ct_df=data.frame(names=names(ct),ct=unname(ct))

# plot
  ggplot(ct_df, aes(x=reorder(names,ct),y=ct)) + geom_bar(stat = 'identity', fill = "salmon", color ="white")+ coord_flip() + theme(axis.text.x = element_text(angle=90, hjust=1))
```

```{r}
 ggplot(mean_social_group1_6cluster, aes(x=reorder(category,frequency),y=frequency)) + geom_bar(stat = 'identity', fill = "salmon", color ="white")+ coord_flip() + theme(axis.text.x = element_text(angle=90, hjust=1))


```

> category: college_uni, online_gaming
> market segmentation: univeristy students, especially boys

```{r}
#plot each group: group 2

#sort the frequency for each category
mean_social_group2_6cluster = apply(social_group2_6cluster, MARGIN=2, FUN=mean)
mean_social_group2_6cluster= sort(mean_social_group2_6cluster, decreasing = TRUE)
mean_social_group2_6cluster = data.frame(cbind(names(mean_social_group2_6cluster),unname(mean_social_group2_6cluster)))

colnames(mean_social_group2_6cluster) <- c("category", "frequency")
mean_social_group2_6cluster$frequency <- as.numeric(as.character(mean_social_group2_6cluster$frequency))

# plot
ggplot(mean_social_group2_6cluster, aes(x=reorder(category,frequency),y=frequency)) + geom_bar(stat = 'identity', fill = "salmon", color ="white")+ coord_flip() + theme(axis.text.x = element_text(angle=90, hjust=1))
```

> category: sports_fandom, religion, food, parenting
> market segmentation: young parents

```{r}
#plot each group: group 3

#sort the frequency for each category
mean_social_group3_6cluster = apply(social_group3_6cluster, MARGIN=2, FUN=mean)
mean_social_group3_6cluster= sort(mean_social_group3_6cluster, decreasing = TRUE)
mean_social_group3_6cluster = data.frame(cbind(names(mean_social_group3_6cluster),unname(mean_social_group3_6cluster)))

colnames(mean_social_group3_6cluster) <- c("category", "frequency")
mean_social_group3_6cluster$frequency <- as.numeric(as.character(mean_social_group3_6cluster$frequency))

# plot
ggplot(mean_social_group3_6cluster, aes(x=reorder(category,frequency),y=frequency)) + geom_bar(stat = 'identity', fill = "salmon", color ="white")+ coord_flip() + theme(axis.text.x = element_text(angle=90, hjust=1))
```

> category: health_nutrition, personal_fitness, cooking, outdoors, photo_sharing
> market segmentation: people who cares fitness

```{r}
#plot each group: group 4

#sort the frequency for each category
mean_social_group4_6cluster = apply(social_group4_6cluster, MARGIN=2, FUN=mean)
mean_social_group4_6cluster= sort(mean_social_group4_6cluster, decreasing = TRUE)
mean_social_group4_6cluster = data.frame(cbind(names(mean_social_group4_6cluster),unname(mean_social_group4_6cluster)))

colnames(mean_social_group4_6cluster) <- c("category", "frequency")
mean_social_group4_6cluster$frequency <- as.numeric(as.character(mean_social_group4_6cluster$frequency))

# plot
ggplot(mean_social_group4_6cluster, aes(x=reorder(category,frequency),y=frequency)) + geom_bar(stat = 'identity', fill = "salmon", color ="white")+ coord_flip() + theme(axis.text.x = element_text(angle=90, hjust=1))
```

> category: politics, travel, news
> market segmentation: well-educated people, especailly male

```{r}
#plot each group: group 5

#sort the frequency for each category
mean_social_group5_6cluster = apply(social_group5_6cluster, MARGIN=2, FUN=mean)
mean_social_group5_6cluster= sort(mean_social_group5_6cluster, decreasing = TRUE)
mean_social_group5_6cluster = data.frame(cbind(names(mean_social_group5_6cluster),unname(mean_social_group5_6cluster)))

colnames(mean_social_group5_6cluster) <- c("category", "frequency")
mean_social_group5_6cluster$frequency <- as.numeric(as.character(mean_social_group5_6cluster$frequency))

# plot
ggplot(mean_social_group5_6cluster, aes(x=reorder(category,frequency),y=frequency)) + geom_bar(stat = 'identity', fill = "salmon", color ="white")+ coord_flip() + theme(axis.text.x = element_text(angle=90, hjust=1))
```

> category: cooking, photo_sharing, fashion, beauty
> market segmentation: young ladies

```{r}
#plot each group: group 6

#sort the frequency for each category
mean_social_group6_6cluster = apply(social_group6_6cluster, MARGIN=2, FUN=mean)
mean_social_group6_6cluster= sort(mean_social_group6_6cluster, decreasing = TRUE)
mean_social_group6_6cluster = data.frame(cbind(names(mean_social_group6_6cluster),unname(mean_social_group6_6cluster)))

colnames(mean_social_group6_6cluster) <- c("category", "frequency")
mean_social_group6_6cluster$frequency <- as.numeric(as.character(mean_social_group6_6cluster$frequency))

# plot
ggplot(mean_social_group6_6cluster, aes(x=reorder(category,frequency),y=frequency)) + geom_bar(stat = 'identity', fill = "salmon", color ="white")+ coord_flip() + theme(axis.text.x = element_text(angle=90, hjust=1))
```

> category: photo_sharing, current_events, shopping
> market segmentation: female who like fashion

# In conclusion, 


