---
title: "Marketing_Segment"
author: "Suyi TU"
date: "2017/8/6"
output: md_document
---

```{r setup,echo=FALSE,include=FALSE}
library(proxy)
library(pander)
library(ggplot2)
library(RColorBrewer)
```

```{r}
social_market <- read.csv('~/Documents/SourceTree/STA380/data/social_marketing.csv')
```

> We delete the following four categories in order to make our market segmentation more meaningful, spam, adult, uncategorize, and chatter. Since adult and spam are categories that are supposed to be filtered and contain improper contents, and uncategorize and chatter have no special meanings. Therefore, we delete these four columns. 

```{r}
discard<-c('spam','adult','uncategorize','chatter')
social_market<-social_market[,!names(social_market)%in%discard]
```

> Since certain high-frequency terms have little discriminating power like photo-sharing, we use TF-IDF to recalculate the weight of each term for every follower. TF stands for term-frequency, measuring how frequent a term occurs in a follower's tweets: the more frequent a term occurs, the more important it is to the follower; IDF stands for inverse-document-frequency, measuring how frequent the term occurs in the whole dataset: the more frequent a term occurs, the less important it is to every follower. 

```{r}
#TFIDF
TF<-social_market[,-1]/rowSums(social_market[,-1])
tmp=sort(apply(TF,2,mean),decreasing=TRUE)
EXI_NUM<-apply(social_market[,-1]>0,2,function(x){table(x)['TRUE']})
IDF<-as.numeric(log(nrow(social_market)/EXI_NUM))
TFIDF = data.frame(t(t(TF)*IDF))
```

> We use 'cosine' as a measurement for the similarity. It calculates the cosine of the angle between two vectors It measures difference in orientation instead of magnitude. For example, we have 3 follower A,B,C with features like A={'travelling':10,'cooking':5}, B={'travelling':20,'cooking':10}, C={'travelling':10,'cooking':12}, we would consider A more similar with B than C even though A and C are 'closer'.

```{r}
#hclust
d.cosine<-dist(TFIDF,method='cosine')
hc.ratio.cosine<-hclust(d.cosine,method='ward.D2')
```

> By looking at different outputs of different Ks, we chose k=3 as our final parameter since its output makes more sense to us.

```{r}
#hclust
#choose cluster 3
out.cluster = cutree(hc.ratio.cosine,k=3)
TFIDF['cluster'] = out.cluster
tfidf<-c()
names<-c()
for(j in 1:3){
    cate = sort(apply(TFIDF[TFIDF['cluster']==j,-ncol(TFIDF)],2,mean),decreasing=TRUE)[1:5]
    name = names(cate)
    tfidf<-c(tfidf,unname(cate))
    names<-c(names,name)
}
cate.df = data.frame(names=names,tfidf_scores=tfidf,cluster=c(rep('A',length(tfidf)/3),rep('C',length(tfidf)/3),rep('B',length(tfidf)/3)))
cate.df$names<-factor(cate.df$names, levels=unique(cate.df$names))

colourCount = length(unique(cate.df$names))
getPalette = colorRampPalette(brewer.pal(11, "Spectral"))

ggplot(cate.df,mapping=aes(x=cluster,y=tfidf_scores,fill=names))+geom_bar(stat='identity',position='dodge')+theme(panel.grid.minor=element_blank(),panel.grid.major=element_blank())+scale_fill_manual(values=getPalette(colourCount))+theme_bw()

names_df<-data.frame('A'=cate.df$names[cate.df$cluster=='A'],'B'=cate.df$names[cate.df$cluster=='B'],'C'=cate.df$names[cate.df$cluster=='C'])
pander(names_df)
```
> From the topics of high TFIDF-socres in the clusters, we can infer that first cluster represents people who care a lot about health, mostly likely housewives; the second cluster represents college/high school students; the third cluster represents people who care about current events, most likely working people.
> yue: what kind of marketing strategies?


